%%%% IACR Transactions TEMPLATE %%%%
% This file shows how to use the iacrtrans class to write a paper.
% Written by Gaetan Leurent gaetan.leurent@inria.fr (2020)
% Public Domain (CC0)


%%%% 1. DOCUMENTCLASS %%%%
\documentclass[journal=tosc,preprint]{iacrtrans}
%%%% NOTES:
% - Change "journal=tosc" to "journal=tches" if needed
% - Change "submission" to "final" for final version
% - Add "spthm" for LNCS-like theorems


%%%% 2. PACKAGES %%%%
\usepackage{lipsum} % Example package -- can be removed
\usepackage{tikz} % For drawing the arrow
\usepackage{tcolorbox}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{graphicx} % For including images
\usepackage{subcaption} % For subfigures and subcaptions


\usetikzlibrary{matrix, positioning}

\lstset{
    basicstyle=\ttfamily\footnotesize,
    keywordstyle=\bfseries\color{blue},
    frame=single, % Adds a border
    numbers=false, % Line numbers
    numberstyle=\tiny\color{gray},
    commentstyle=\color{green!60!black},
    stringstyle=\color{orange},
    showstringspaces=false,
    breaklines=true,
    backgroundcolor=\color{gray!10},
}

%%%% 3. AUTHOR, INSTITUTE %%%%
\author{Lalit Gour\inst{1,2} \and Vedant Udan\inst{1,3} \and Karan Sunil Kumbhar\inst{1,4}}
% \institute{
%   Indian Institute of Technology Bhilai, India, \email{lalitg@iitbhilai.ac.in}
%   \and
%   Indian Institute of Technology Bhilai, India, \email{udanvedant@iitbhilai.ac.in}
%   \and
%   Indian Institute of Technology Bhilai, India, \email{karansunilk@iitbhilai.ac.in}
% }

\newcommand{\iitbhilai}{Indian Institute of Technology Bhilai, India}

% \author{
%   Lalit Gour\inst{1} \and Vedant Udan\inst{1} \and Karan Sunil Kumbhar\inst{1}
% }
\institute{
  \iitbhilai \and \email{lalitg@iitbhilai.ac.in} \and
  \email{udanvedant@iitbhilai.ac.in} \and
  \email{karansunilk@iitbhilai.ac.in} 
}


%%%% NOTES:
% - We need a city name for indexation purpose, even if it is redundant
%   (eg: University of Atlantis, Atlantis, Atlantis)
% - \inst{} can be omitted if there is a single institute,
%   or exactly one institute per author


%%%% 4. TITLE %%%%
\title{Midori - Implementation and Analysis}
%%%% NOTES:
% - If the title is too long, or includes special macro, please
%   provide a "running title" as optional argument: \title[Short]{Long}
% - You can provide an optional subtitle with \subtitle.

\begin{document}

\maketitle


%%%% 5. KEYWORDS %%%%
\keywords{Midori64 \and DDT/LAT analysis \and Integral Cryptanalysis \and Differential Crytanalysis \and MILP Model}


%%%% 6. ABSTRACT %%%%
\begin{abstract}

    In this paper we discuss the algorithm to implement Midori Cipher perform
    Integral and Differential Cryptanalysis on it.

\end{abstract}


%%%% 7. PAPER CONTENT %%%%
\section{Introduction}

The Midori cipher, introduced by Banik et al. in 2015, is a lightweight block
cipher specifically designed for resource-constrained environments such as IoT
devices and embedded systems. It emphasizes energy efficiency and low power
consumption while ensuring robust security against standard cryptographic
attacks. Midori comes in two variants: Midori-64 (64-bit block size, 128-bit
key) and Midori-128 (128-bit block size, 128-bit key), both based on a
Substitution-Permutation Network (SPN) structure. By employing simple operations
like XOR, substitution (S-box), and diffusion via MixColumn, Midori achieves
high energy efficiency and compact hardware implementation, making it
well-suited for applications in smart cards, wearables, and RFID systems. While
its lightweight design balances security and performance, its reduced complexity
compared to heavyweight ciphers like AES may make it vulnerable to advanced
attack scenarios.

\section{Integral Cryptanalysis}
Similar to Differential but here we use a Set of Plaintexts known as Delta Set (\(\Delta\)) instead of just two.
\subsection{Basic Knowledge }
\subsubsection{Definition of Integral Property}
\begin{itemize}
    \item \textbf{Constant \( \mathcal{C} \)}: The constant byte is constant whose value is fixed and unchanged.
    \item \textbf{Active \( \mathcal{A} \)}: Bytes traverse all values of 0 - 15, which is called active byte.
    \item \textbf{Balance \( \mathcal{B} \)}: The sum of bytes is 0, which is called balanced byte.
    \item \textbf{Unknown \( \mathcal{U} \)}: If the nature of a byte is uncertain, it is called an unknown byte.
\end{itemize}
The linear combination of active bytes \( \mathcal{A} \) and constant
bytes \( \mathcal{C} \) is active byte \( \mathcal{A} \). The constant bytes \( \mathcal{C} \) and
balance bytes \( \mathcal{B} \) are balance \( \mathcal{B} \) after the linear operation.
Independent active bytes \( \mathcal{A} \) is active \( \mathcal{A} \) after linear
combination. The linear combination of two related active \( \mathcal{A} \)
is balance \( \mathcal{B} \). Balance \( \mathcal{B} \) changes into unknown \( \mathcal{U} \) through
nonlinear bijection. Active \( \mathcal{A} \) has the characteristics of
penetration to S-box and AddRoundKey. And so on.
\subsubsection{Delta Set (\(\Delta\)) }
\begin{itemize}
    \item We will be taking a Set of 16 Plaintexts called Delta Set (\(\Delta\)) where 4 bits of each plaintext takes all values from \( \{0, 1\}^4 \) and the rest of the 60 bits have constant values.
    \item In case of Midori64 Bit Block we get the following:
          \[
              P_0 = (0, c_1, c_2, \dots, c_{14}, c_{15}),
          \]
          \[
              P_1 = (1, c_1, c_2, \dots, c_{14}, c_{15}),
          \]
          \[
              \vdots
          \]
          \[
              P_{15} = (15, c_1, c_2, \dots, c_{14}, c_{15}),
          \]

          and the Delta Set (\( \Delta \)) is defined as:

          \[
              \Delta = \{P_0, P_1, \dots, P_{15}\}.
          \]

    \item The Initial Plaintext Set (\(\Delta\)) in terms of \( \mathcal{A} \), \( \mathcal{C} \) and \( \mathcal{B} \).

          \[
              \Delta = \{\( \mathcal{A} \), \( \mathcal{C} \),\( \mathcal{C} \), \dots, \( \mathcal{C} \)\}.
          \]

\end{itemize}
\subsubsection{Symbol}

The meaning of the symbolic representation below:

\begin{align*}
    s_j^{(i)} & : \text{The } j\text{-th byte of the } i\text{-th round input.}      \\
    m_j^{(0)} & : \text{The } j\text{-th byte of the plaintext.}                     \\
    c_j^{(i)} & : \text{The } j\text{-th byte in the } i\text{-th round ciphertext.} \\
    k_j^{(i)} & : \text{The } j\text{-th byte in the } i\text{-th round key.}        \\
    R_i       & : \text{The } i\text{-th round.}
\end{align*}


\subsection{Description of Midori}
Midori is a lightweight block ciphers which follows the
Substitution-Permutation Network (SPN) design approach.
The grouping of the Midori algorithm expressed by State
Matrix and Each element in the matrix is a Cell. The State
Matrix is a 4 × 4 matrix, as shown in Fig. 1. For the two
algorithms which have different packet length, each Cell
contains different vector lengths. The length of each Cell of
the Midori64 is 4-bit. The length of each Cell of the
Midori128 is 8-bit. And the unified definition of the left end
of each Cell vector is MSB, the right end of each Cell vector
is LSB.



\[
    \begin{bmatrix}
        S_{0} & S_{4} & S_{8}  & S_{12} \\
        S_{1} & S_{5} & S_{9}  & S_{13} \\
        S_{2} & S_{6} & S_{10} & S_{14} \\
        S_{3} & S_{7} & S_{11} & S_{15}
    \end{bmatrix}
\]

\begin{center}
    Fig.1 : State matrix of midori.
\end{center}

\subsubsection{SubCell (\( \mathcal{S} \))}

The S-box type of Midori used by 4-bit S-box. The 4-bit
S-boxes is shown in TABLE I. The S-boxes of Midori64 correspond to ${S_0(x)}

    \begin{table}[h!]
        \centering
        \begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|}
            \hline
            x          & 0 & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & a & b & c & d & e & f \\ \hline
            ${S_0(x)}$ & c & a & d & 3 & e & b & f & 7 & 8 & 9 & 1 & 5 & 0 & 2 & 4 & 6 \\ \hline
        \end{tabular}
        % \caption{A \(2 \times 5\) table.}
        \label{tab:example}
    \end{table}


    \subsubsection{SuffleCell (\( \mathcal{SC} \))}
    The change of the position of each Cell in the
    replacement process of the State Matrix is shown in Fig. 3.

    \[
        \renewcommand{\arraystretch}{1.5} % Adjust the row height
        \setlength{\tabcolsep}{0pt} % Remove extra padding between columns
        \begin{array}{|c|c|c|c|}
            \hline
            S_{0} & S_{4} & S_{8}  & S_{12} \\ \hline
            S_{1} & S_{5} & S_{9}  & S_{13} \\ \hline
            S_{2} & S_{6} & S_{10} & S_{14} \\ \hline
            S_{3} & S_{7} & S_{11} & S_{15} \\ \hline
        \end{array}
        \quad
        \begin{tikzpicture}[baseline=(current bounding box.center)]
            \draw[->, thick] (0,0) -- (2.5,0) node[midway, above] {ShuffleCell};
        \end{tikzpicture}
        \quad
        \begin{array}{|c|c|c|c|}
            \hline
            S_{0}  & S_{14} & S_{9}  & S_{7}  \\ \hline
            S_{10} & S_{4}  & S_{3}  & S_{13} \\ \hline
            S_{5}  & S_{11} & S_{12} & S_{2}  \\ \hline
            S_{15} & S_{1}  & S_{6}  & S_{8}  \\ \hline
        \end{array}
    \]
    \begin{center}
        Fig.3 : ShuffleCell.
    \end{center}

    The inverse of ShuffleCell (SC) is shown in Fig. 4.

    \[
        \renewcommand{\arraystretch}{1.5} % Adjust the row height
        \setlength{\tabcolsep}{0pt} % Remove extra padding between columns
        \begin{array}{|c|c|c|c|}
            \hline
            S_{0} & S_{4} & S_{8}  & S_{12} \\ \hline
            S_{1} & S_{5} & S_{9}  & S_{13} \\ \hline
            S_{2} & S_{6} & S_{10} & S_{14} \\ \hline
            S_{3} & S_{7} & S_{11} & S_{15} \\ \hline
        \end{array}
        \quad
        \begin{tikzpicture}[baseline=(current bounding box.center)]
            \draw[->, thick] (0,0) -- (2.5,0) node[midway, above] {ShuffleCell$^{-1}$};
        \end{tikzpicture}
        \quad
        \begin{array}{|c|c|c|c|}
            \hline
            S_{0}  & S_{5}  & S_{15} & S_{10} \\ \hline
            S_{7}  & S_{2}  & S_{8}  & S_{13} \\ \hline
            S_{14} & S_{11} & S_{1}  & S_{4}  \\ \hline
            S_{9}  & S_{12} & S_{6}  & S_{3}  \\ \hline
        \end{array}
    \]
    \begin{center}
        Fig.4 : ShuffleCell$^{-1}$
    \end{center}

    \subsubsection{MixColumn (\( \mathcal{MC} \))}
    The Cell vector in each column of State Matrix multiplies
    with a constant 4 × 4 binary matrix M, where M as given below:

    \begin{equation}
        \begin{bmatrix}
            0 & 1 & 1 & 1 \\
            1 & 0 & 1 & 1 \\
            1 & 1 & 0 & 1 \\
            1 & 1 & 1 & 0
        \end{bmatrix}
        \tag{1}
    \end{equation}

    \subsubsection{KeyAdd (\( \mathcal{S} \), \( \mathcal{RK$_{i}$} \)) }
    It is used bit-oriented. First, we should write round key as
    in (1) according to the rules. Second, the i-th m-bit round key
    RK$_{i}$ is XORed to m-bit of State Matrix S.


    \subsubsection{Key Schedule}
    The key schedule of Midori whose design is very simple.
    The whiten key WK in Midori are the initial key K, as in (3)
    \begin{equation}
        WK = K
        \tag{3}
    \end{equation}
    For the Midori64 algorithm, the initial key is divided into
    two 64-bit keys, that is K$_{0}$ and K$_{1}$ as K = K$_{0}$ || K$_{1}$. The sub-key
    of Midori64 for round i is K$_{i} = K$_{i mod 2} \oplus \( \mathcal{B$_{i}} \)

    \subsection{6 - Round integral distinguiser of midori}
    First, constructing a 4-round integral distinguisher in the
    direction of encryption with an active byte as shown in Fig. 5.

    % attack 6 round 
    \input{texFiles/Fig5_integral_6_round_attack.tex}

    \begin{center}
        Fig.5 : 4-Round integral distinguishers on Midori.
    \end{center}

    Second, constructing a 2-round integral distinguisher in
    the direction of decryption as shown in Fig. 6

    % attack 2 round
    \input{texFiles/Fig6_integral_2_round_attack.tex}
    \begin{center}
        Fig.6 : 6-Round integral distinguishers on Midori.
    \end{center}

    Lemma 1: Taking nine 4 bits  cells in plaintext state S$_1{^0}$ ,
    S$_2{^0}$ ,
    S$_3{^0}$ ,
    S$_6{^0}$ ,
    S$_7{^0}$ ,
    S$_9{^0}$ ,
    S$_{11}{^0}$ ,
    S$_{13}{^0}$ ,
    S$_{14}{^0}$ as active A that
    traverse all values, and other 4 bits cells are constants C. After two
    rounds of encryption, we get $2^{32}$ sets and in each set the byte
    of S$_0{^2}$ will traverse all values, and the other bytes are
    constants C.

    Proof. It's just a case of proving when S$_1}$, S$_2}$, S$_3}$ take all
    values in equation given below. After $2^{12}$ vectors $(0, S$_1}$, S$_2}$, S$_3}$)^T$ are
    transformed by MixColumn(MC), $2^{8}$ sets are obtained and
    the first component of each set takes all values of 0 to 15 and
    others are constants C.


    \[
        \begin{bmatrix}
            0 & 1 & 1 & 1 \\
            1 & 0 & 1 & 1 \\
            1 & 1 & 0 & 1 \\
            1 & 1 & 1 & 0 \\
        \end{bmatrix}
        \begin{bmatrix}
            0     \\
            S$_1$ \\
            S$_2$ \\
            S$_3$ \\
        \end{bmatrix}
        =
        \begin{bmatrix}
            S$_1$ \oplus S$_2$ \oplus S$_3$ \\
            S$_2$ \oplus S$_3$              \\
            S$_1$  \oplus S$_3$             \\
            S$_1$ \oplus S$_2$              \\
        \end{bmatrix}
    \]


    Let $S_1$ \oplus $S_2$ \oplus $S_3$ = $t_1$, S$_2$ \oplus S$_3$ = $t_2$, S$_1$ \oplus S$_3$ = $t_3$ which vectors
    are pairwise independence. The fourth vector is S$_1$ \oplus S$_2$ = t$_1$ \oplus t$_2$  that is the linear combination of the second
    component and the third component. Therefore, when S$_2$ ,S$_3$ are  constants  the first vector in the set takes all values of
    0 to 15. This collection has a total of $2^8$.
    This property is applied to the first round and second
    round of transformation, so we get the Lemma 1

    \newpage
    \section{S-box Analysis of Midori64}
    \input{texFiles/DDT_Analysis.tex}

    \section*{Acknowledgment}
    In this term paper, we have not implemented the MILP (Mixed Integer Linear
    Programming) model for differential trail generation. Instead, we have
    referred directly to the results presented in the paper titled "MILP-Based
    Differential Cryptanalysis on Round-Reduced Midori64" by Jiageng Cheng,
    Xinyu Sun, and Meiqin Wang. For further details on the MILP trails, please
    see the original paper available at MILP-Based Differential Cryptanalysis on
    Round-Reduced Midori64. \cite{zhao2020}


    \newpage
    \section{Differential Attack on 11-Round Midori64}

    \subsection{The Property of Probability for Round Function}

    \textbf{Property 1:} Consider four cells of the intermediate state of SC with any input difference and any output difference. However, we want one cell of these four with zero difference after the MC operation. For example, let $X\{3, 6, 9, 12\}$ denote the positions (3, 6, 9, 12) before the SC operation, and $Y\{3, 6, 9, 12\}$, $Z\{8, 9, 10, 11\}$, $W\{8, 9, 10, 11\}$ denote the corresponding positions after SC, SFC, and MC operations, respectively. Let $\Delta w_{11} = 0$, then $\Delta z_8 = \Delta z_9 \oplus \Delta z_{10}$ with the probability of $\frac{1}{16} = 2^{-4}$. Let $P((?, ?, ?, ?) \to (?, ?, ?, 0))$ denote $P(\text{SC}(?, ?, ?, ?) \to \text{MC}(?, ?, ?, ?) = (?, ?, ?, 0))$. So, $P((?, ?, ?, ?) \to (?, ?, ?, 0)) = 2^{-4}$. Since $? \in \{0, 1, \dots, 15\}$ and $\ast \in \{1, 2, \dots, 15\}$, we can obtain $P((?, ?, ?, ?) \to (?, ?, \ast, 0)) = \frac{15}{16} \cdot \frac{1}{16} \approx 2^{-4.09}$. Similarly, $P((?, ?, ?, ?) \to (?, \ast, \ast, 0)) \approx 2^{-4.19}$, and $P((?, ?, ?, ?) \to (\ast, \ast, \ast, 0)) \approx 2^{-4.28}$.

    \textbf{Property 2:} Consider four cells of the intermediate state of SC with any input difference and any output difference. However, we want no less than one cell of these four with non-zero difference after the MC operation. We can obtain $P((?, ?, ?, ?) \to (?, ?, ?, \ast)) = \frac{15}{16} \approx 2^{-0.09}$. Similarly, $P((?, ?, ?, ?) \to (?, ?, \ast, \ast)) \approx 2^{-0.19}$, and $P((?, ?, ?, ?) \to (?, \ast, \ast, \ast)) \approx 2^{-0.28}$.

    \textbf{Property 3:} Consider four cells of SC with two arbitrary input differences and two non-zero differences; then, we want to get two zero differences after the MC operation. We can obtain $P((?, ?, \ast, \ast) \to (\ast, \ast, 0, 0)) = \frac{1}{16} \cdot \frac{1}{16} = 2^{-8}$ and $P((?, ?, \ast, \ast) \to (?, ?, 0, 0)) \approx 2^{-7.81}$.

    \textbf{Property 4:} If there are three cells with any or any non-zero input differences of SC and the same non-zero output differences of SC, we can obtain $P((?, ?, ?, 0) \to (11, 0, 0, 0)) = \frac{15}{16} \cdot \frac{1}{16} \cdot \frac{1}{16} \approx 2^{-8.09}$ and $P((\ast, \ast, \ast, 0) \to (12, 0, 0, 0)) \approx 2^{-7.81}$.

    \begin{table}[h!]
        \centering
        \caption{5-round differential path of Midori64 with probabilities $2^{-52}$ and $2^{-58}$.}
        \begin{tabular}{@{}clclc@{}}
            \toprule
            \textbf{Input Round} & \textbf{Input Differential-1}    & \textbf{Probability} & \textbf{Input Differential-2} & \textbf{Probability} \\ \midrule
            1                    & $\alpha$000 0000 00$\beta$0 0000 & 1                    & $\delta$000 0000 0000 0000    & 1                    \\
            2                    & 2200 0000 0000 0000              & $2^{-4}$             & 0AAA 0000 0000 0000           & $2^{-2}$             \\
            3                    & 0440 1110 0000 0000              & $2^{-8}$             & 0000 5550 A0AA AA0A           & $2^{-8}$             \\
            4                    & 2202 0202 0202 2202              & $2^{-20}$            & 05AF 0AA0 AA7D 0A0A           & $2^{-26}$            \\
            5                    & 0400 0011 0001 1100              & $2^{-40}$            & 5000 0077 00A0 5000           & $2^{-48}$            \\
            6                    & 0000 0022 0032 2200              & $2^{-52}$            & AA00 0000 FF5A 0555           & $2^{-58}$            \\ \bottomrule
        \end{tabular}
        \vspace{0.3cm}
        \begin{flushleft}
            $\alpha, \beta \in \{1,4,9,C\}$ and $\delta \in \{5,A,D,F\}.$
        \end{flushleft}
    \end{table}
    \newpage
    %  fig 1 differential attack
    \input{texFiles/Fig1_differential_5_round_attack_1.tex}

    where $\delta \in \{5, A, D, F\}$
    \newline

    % %======================================================================================================

    %  fig 1 differential attack
    \input{texFiles/Fig2_differential_5_round_attack_2.tex}

    \subsection{Attack on 11-Round Midori64}

    Using the 5-round differential characteristic

    % (\delta, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0) \to (A, A, 0, 0, 0, 0, 0, 0, F, F, 5, A, 0, 5, 5, 5)
    \begin{center}
        \begin{tikzpicture}[node distance=0.01cm and 0cm]
            \node[minimum width=6cm, align=center] (tuple1)
            {(\(\delta, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0\))};
            \node[below=of tuple1, align=center] (arrow) {\(\downarrow\)};
            \node[minimum width=6cm, below=of arrow, align=center] (tuple2)
            {(\(A, A, 0, 0, 0, 0, 0, 0, F, F, 5, A, 0, 5, 5, 5\))};
        \end{tikzpicture}
    \end{center}
    with the probability of $2^{-58}$ in Table 1 and Figure 1, we could launch a key-recovery attack against the 11-round Midori64. We choose the differential-2 rather than the differential-1 because the former is more effective.

    Then, add three rounds at its beginning and the end, respectively, to attack the 11-round reduced Midori64, as shown in Figure 2. The attack procedures are as follows:

    \subsubsection{Data Collection}
    Since the differences of plaintexts are all uncertain bits, plaintexts cannot be classified by inactive bits. Choose any $2^n$ plaintexts and form approximately $2^{2n-1}$ plaintext pairs. Encrypt these plaintext pairs to state $W_1$ and use the difference $\Delta W_1\{0, 1, 2, 3\} = \{0, \ast, \ast, \ast\}$ to filter pairs. By Property 1, this provides a filtering probability of $2^{-4.28}$, and there are approximately $2^{2n-5.28}$ pairs left. Similarly, keep only the pairs such that $\Delta W_1 \{4, 5, 6, 7\} = \{0, 0, \ast, \ast \}, \Delta W_1 \{8, 9, 10, 11\} = \{0, \ast, 0, \ast \}$ and $\Delta W_1 \{12, 13, 14, 15\} = \{0, \ast, \ast, 0\}$. By Property 3, the probability of these three cases is $2^{-8}$ and there are $2^{2n - 29.28}$ pairs left. Therefore, in the data collection phase, the remaining number jof the plaintext/cipertext paires is approximately $2^{2n - 29.28}$ only by the path choosing without guessing the key.
    \input{texFiles/11_round_differential_attack.tex}

    \subsubsection{Key Recovery}

    \begin{enumerate}
        \item \textbf{Guess 12 bits $K_0\{1, 11, 14\} \oplus \alpha_0\{1, 11, 14\}$:}
              Partially encrypt these plaintext pairs. The middle values of the correct pairs should satisfy
              \[
                  \Delta X_2\{1, 4, 11, 14\} = \{\ast, 0, \ast, \ast\}, \quad \Delta Y_2\{1, 4, 11, 14\} = \{\Delta_1, 0, \Delta_1, \Delta_1\}.
              \]
              the pairs can be filtered with a probability of $2^{-7.81}$ (Property 4), leaving approximately $2^{2n-37.09}$ pairs.
              Similarly, guess $K_0\{2, 7, 13\} \oplus \alpha_0\{2, 7, 13\}$, and the correct pairs should satisfy
              \[
                  \Delta Y_2\{2, 7, 8, 13\} = \{\Delta_2, \Delta_2, 0, \Delta_2\}.
              \]
              Then, guess $K_0\{3, 6, 9\} \oplus \alpha_0\{3, 6, 9\}$, and the correct pairs should satisfy
              \[
                  \Delta Y_2\{3, 6, 9, 12\} = \{\Delta_3, \Delta_3, \Delta_3, 0\}.
              \]
              After these steps, there are approximately $2^{2n-52.71}$ pairs left.

        \item \textbf{Guess 12 bits $K_1\{5, 10, 15\} \oplus \alpha_1\{5, 10, 15\}$:}
              For each remaining pair, guess the 12 bits one by one and partially encrypt these pairs. The correct pairs should satisfy
              \[
                  \Delta Y_3\{5, 10, 15\} = \{\delta, \delta, \delta\}, \quad \delta \in \{5, A, D, F\}.
              \]
              This step has a filtering probability of $2^{-7.81} \cdot \frac{4}{15} \approx 2^{-9.72}$ (Property 4), leaving approximately $2^{2n-62.43}$ pairs.

        \item \textbf{Guess $MC^{-1}(K_0 \oplus \alpha_{10})\{0, 4, 5, 8, 10, 12, 15\}$:}
              Decrypt the remaining pairs to state $W_{10}$. Use the following conditions to filter pairs:
              \[
                  \Delta W_{10}\{0, 1, 2, 3\} = \{?, \ast, ?, \ast\}, \quad \Delta W_{10}\{4, 5, 6, 7\} = \{?, ?, \ast, ?\},
              \]
              \[
                  \Delta W_{10}\{8, 9, 10, 11\} = \{\ast, ?, ?, ?\}, \quad \Delta W_{10}\{12, 13, 14, 15\} = \{?, \ast, ?, 0\}.
              \]
              The filtering probabilities are $2^{-0.19}$, $2^{-0.09}$, $2^{-0.09}$ (Property 2), and $2^{-4.09}$ (Property 1), respectively. After this step, there are approximately $2^{2n-66.89}$ pairs left.

        \item \textbf{Guess $MC^{-1}(K_1 \oplus \alpha_9)\{0, 1, 2, 3, 4, 6, 7, 8, 9, 11, 12, 13, 14\}$:}
              Decrypt the remaining pairs to state $W_9$ and apply the following filtering conditions:
              \[
                  \Delta W_9\{0, 1, 2, 3\} = \{\ast, \ast, 0, \ast\}, \quad \Delta W_9\{4, 5, 6, 7\} = \{\ast, 0, \ast, \ast\},
              \]
              \[
                  \Delta W_9\{8, 9, 10, 11\} = \{\ast, 0, 0, 0\}, \quad \Delta W_9\{12, 13, 14, 15\} = \{0, \ast, 0, \ast\}.
              \]
              The filtering probabilities are $2^{-4.28}$, $2^{-4.28}$ (Property 1), $2^{-7.81}$ (Property 4), and $2^{-8}$ (Property 3), respectively. After this step, there are approximately $2^{2n-91.26}$ pairs left.

        \item \textbf{Final Decryption:}
              Decrypt the remaining pairs to state $X_9$. Use the condition
              \[
                  \Delta X_9\{0, 1, 8, 9, 10, 11, 13, 14, 15\} = \{A, A, F, F, 5, A, 5, 5, 5\}
              \]
              to filter pairs one by one. This final step has a total filtering probability of $2^{-35.19}$. After this step, there are approximately $2^{2n-126.45}$ pairs left.
    \end{enumerate}


    \subsubsection{Complexity Analysis}

    \textbf{Data Complexity:}
    To distinguish the correct key from the wrong ones, choose $n = 61.2$. For a random key, there are approximately $2^{2 \times 61.2 - 126.45} \approx 2^{-4.05}$ pairs left. However, for the correct key, there are $2^{2 \times 61.2 - 62.43 - 58} \approx 4$ pairs left as the probability of the 5-round differential Path is $2^{-58}$. Thus, the data complexity is $2^{61.2}$ chosen plaintexts.\\
    \newline
    \textbf{Time Complexity:}
    \begin{enumerate}
        \item There are $2^{2n-29.28} = 2^{93.12}$ pairs left after the phase of data collection.
              Guess 12 bits $K_0\{1, 11, 14\} \oplus \alpha_0\{1, 11, 14\}$, then partially encrypt these plaintext pairs for one round.
              The time complexity is
              \[
                  2^{93.12} \times 2 \times 2^{12} \times \frac{3}{16} \times \frac{1}{11} \approx 2^{100.25}
              \]
              11-round encryptions, and the number of remaining pairs is $2^{85.31}$.

              Similarly, guess $K_0\{2, 7, 13\} \oplus \alpha_0\{2, 7, 13\}$, and the time complexity is
              \[
                  2^{85.31} \times 2 \times 2^{12} \times \frac{3}{16} \times \frac{1}{11} \approx 2^{92.44}
              \]
              11-round encryptions, and the number of remaining pairs is $2^{77.5}$.

              Then, guess $K_0\{3, 6, 9\} \oplus \alpha_0\{3, 6, 9\}$, and the time complexity is
              \[
                  2^{84.63}
              \]
              11-round encryptions, and the number of remaining pairs is $2^{69.69}$.

        \item For every remaining pair, guess 12 bits $K_1\{5, 10, 15\} \oplus \alpha_1\{5, 10, 15\}$, and the time complexity is
              \[
                  2^{69.69} \times 2 \times 2^{12} \times \frac{3}{16} \times \frac{1}{11} \approx 2^{76.82}
              \]
              11-round encryptions, and the number of remaining pairs is $2^{59.97}$.

        \item Guess $MC^{-1}(K_0 \oplus \alpha_{10})\{1, 2, 3, 6, 7, 9, 11, 13, 14\}$, and for the whole round, the time complexity is
              \[
                  2^{59.97} \times 2 \times 2^{28} \times \frac{1}{11} \approx 2^{85.51}
              \]
              11-round encryptions, and the number of remaining pairs is $2^{55.51}$.

        \item Similarly, guess $MC^{-1}(K_1 \oplus \alpha_9)\{1, 6, 8\}$, and the time complexity is
              \[
                  2^{55.51} \times 2 \times 2^{12} \times \frac{3}{16} \times \frac{1}{11} \approx 2^{62.64}
              \]
              11-round encryptions, and the number of remaining pairs is $2^{47.7}$.

              Guess $MC^{-1}(K_1 \oplus \alpha_9)\{3, 4, 13\}$, and the time complexity is
              \[
                  2^{47.7} \times 2 \times 2^{12} \times \frac{4}{16} \times \frac{1}{11} \approx 2^{55.24}
              \]
              11-round encryptions, and the number of remaining pairs is $2^{39.7}$.

              Guess $MC^{-1}(K_1 \oplus \alpha_9)\{0, 7, 9, 14\}$, and the time complexity is
              \[
                  2^{39.7} \times 2 \times 2^{16} \times \frac{4}{16} \times \frac{1}{11} \approx 2^{51.24}
              \]
              11-round encryptions, and the number of remaining pairs is $2^{35.42}$.

              Guess $MC^{-1}(K_1 \oplus \alpha_9)\{2, 11, 12\}$, and the time complexity is
              \[
                  2^{35.42} \times 2 \times 2^{12} \times \frac{3}{16} \times \frac{1}{11} \approx 2^{42.55}
              \]
              11-round encryptions, and the number of remaining pairs is $2^{31.14}$.

        \item Finally, the time complexity is
              \[
                  2^{31.14} \times 2 \times \frac{9}{16} \times \frac{1}{11} \approx 2^{27.85}
              \]
              11-round encryptions.

              Thus, the total time complexity is
              \[
                  2^{100.26}
              \]
              11-round encryptions.
    \end{enumerate}


    \subsection{Complexity Analysis of another differential path with probability of $2^{-52}$}

    Similarly, add 3 rounds at the beginning and at the end of the differential
    path with a probability of $2^{-52}$ to attack the 11-round reduced
    Midori64. It is easy to get the probability of $2^{-56.18}$ for the top 3
    rounds.

    Thus, we choose $n = 55.6$. For a random key, there are approximately
    \[
        2^{2 \times 55.6 - 1 - 56.18 - 64} \approx 2^{-10}
    \]
    pairs left. However, for the correct key, there are
    \[
        2^{2 \times 55.6 - 1 - 56.18 - 52} \approx 4
    \]
    pairs left, as the probability of the 5-round differential path is $2^{-52}$.

    Therefore, the data complexity is $2^{55.6}$ chosen plaintexts, and the time
    complexity is $2^{109.35}$ 11-round encryptions, correspondingly.

\newpage
\section{MILP Model}
\input{texFiles/milp_model.tex}
%%%% 8. BILBIOGRAPHY %%%%
\bibliographystyle{alpha}
\bibliography{main}


\end{document}
